Exploring the evolution of stellar rotation using Galactic kinematics

### 2020-04-23 paper/ms63.tex
jen's comments

\author{Jennifer van Saders}
\affiliation{Institute for Astronomy, University of Hawai`i, 2680
Woodlawn Drive, Honolulu, HI 96822, USA}

@@

The \citet{angus2019} relation is a new fully-empirical gyrochronology
relation, calibrated using recently measured rotation periods for members of
the Praesepe cluster, which extend down to early M dwarfs \citep{rebull2017,
douglas2017}.
These are the oldest cluster M dwarfs with measured photometric rotation
periods and the \citet{angus2019} model therefore encapsulates the behavior of
these cool stars at Praesepe age.
Most semi-physical spin-down models predict that, once the rotation periods of
stars converge to a tight sequence, they approximately spin down with a common
braking index \citep[e.g., Fig. 5 in][]{gallet2015}.
While some semi-physical models do not predict that stars have fully converged
by the age of Praesepe, the observations suggest that they have
\citep{douglas2019}, in which case, projecting the Praesepe sequence forward
with a single braking index that is common to all stars and constant in time
is appropriate.
However, observations of low-mass stars in older clusters \citep[\eg, NGC
6811, NGC 752, and Ruprecht 147][Curtis \etal, submitted]{curtis2019,
agueros2018} demonstrate that the assumptions adopted in those models must be
invalid, or inaccurate in some quantitative way (for example, the
core-envelope coupling timescale is inaccurately calibrated).

>>>>

\author[0000-0002-4284-8638]{Jennifer van Saders}
\affiliation{Institute for Astronomy, University of Hawai`i, 2680
Woodlawn Drive, Honolulu, HI 96822, USA}

@@

The \citet{angus2019} relation is a new fully-empirical gyrochronology
relation, calibrated using recently measured rotation periods for members of
the Praesepe cluster, which extend down to early M dwarfs \citep{rebull2017,
douglas2017}.
These are the oldest cluster M dwarfs with measured photometric rotation
periods and the \citet{angus2019} model therefore encapsulates the behavior of
these cool stars at Praesepe age.
Most semi-empirical spin-down models predict that, once the rotation periods of
stars converge to a tight sequence, they approximately spin down with a common
braking index \citep[e.g., Fig. 5 in][]{gallet2015}.
While some semi-empirical models do not predict that stars have fully converged
by the age of Praesepe, the observations suggest that they have
\citep{douglas2019}, in which case, projecting the Praesepe sequence forward
with a single braking index that is common to all stars and constant in time
is appropriate.
However, observations of low-mass stars in older clusters \citep[\eg, NGC
6811, NGC 752, and Ruprecht 147][Curtis \etal, submitted]{curtis2019,
agueros2018} demonstrate that the assumptions adopted in those models must be
invalid, or inaccurate in some quantitative way (for example, the
core-envelope coupling timescale is inaccurately calibrated).
